\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-05-27 Supplement.tex
edits
reformatting tables for \longtable
edits
working on table formatting

% Table S1. Parv and mex samples 
\setlength\LTleft{-30pt}            
\setlength\LTright{-30pt}
\begin{longtable}{ccp{5cm}cp{5cm}ccc}

@@

 \textbf{Accession} & \textbf{USDA ID} & \textbf{Locality} & \textbf{Number Alleles Sampled} & \textbf{\emph{Hopscotch} Frequency} & \textbf{No \emph{Hopscotch} Frequency} \\\toprule

@@

    RIMPA0069 & 699862 & Ixtlan & 14    & 0.142857143 & 0.857142857 \\

@@

    RIMPA0073 & 699866 & Tiquicheo & 16    & 0.125 & 0.875 \\

@@

    RIMPA0086 & 699880 & Miahuatlan & 16    & 0.0625 & 0.9375 \\

@@

    RIMPA0093 & 699887 & Guerrero & 26    & 0.076923077 & 0.923076923 \\

@@

    RIMPA0096 & 699890 & Guerrero & 26    & 0.038461538 & 0.961538462 \\

@@

    RIMPA0104 & 699898 & Guerrero & 22    & 0.090909091 & 0.909090909 \\

@@

    RIMPA0106 & 699900 & Guerrero & 6     & 0.333333333 & 0.666666667 \\

@@

    RIMPA0114 & 699908 & Michoacan & 6     & 0.166666667 & 0.833333333 \\

@@

    RIMPA0118 & 699912 & Mexico & 6     & 0.166666667 & 0.833333333 \\

@@

    RIMPA0142 & 699936 & Colima & 18    & 0.444444444 & 0.555555556 \\

@@

    RIMPA0155 & N/A   & Jalisco & 73    & 0.01369863 & 0.98630137 \\

@@

    RIMPA0157 & N/A   & Jalisco & 58    & 0.344827586 & 0.655172414 \\
    RIMPA0158 & N/A   & Jalisco & 64    & 0.53125 & 0.46875 \\

@@

% Table S3. PCs for BayEnv

>>>>

% Table S2. Parv and mex samples 
\footnotesize  % Switch from 12pt to 11pt; otherwise, table won't fit
\setlength\LTleft{-30pt}            % default: \fill
\setlength\LTright{-30pt}           % default: \fill
\begin{longtable}{@{\extracolsep{\fill}}llllllllll@{}}
  \hline\hline %inserts double horizontal lines

@@

 \textbf{Accession} & \textbf{USDA ID} & \textbf{Locality} & \textbf{\# Alleles Sampled} & \textbf{\emph{Hopscotch} Frequency} & \textbf{No \emph{Hopscotch} Frequency} \\\toprule

@@

    RIMPA0069 & 699862 & Ixtlan & 14    & 0.14 & 0.86 \\

@@

    RIMPA0073 & 699866 & Tiquicheo & 16    & 0.12 & 0.88 \\

@@

    RIMPA0086 & 699880 & Miahuatlan & 16    & 0.06 & 0.94 \\

@@

    RIMPA0093 & 699887 & Guerrero & 26    & 0.08 & 0.92 \\

@@

    RIMPA0096 & 699890 & Guerrero & 26    & 0.04 & 0.96 \\

@@

    RIMPA0104 & 699898 & Guerrero & 22    & 0.09 & 0.91 \\

@@

    RIMPA0106 & 699900 & Guerrero & 6     & 0.33 & 0.67 \\

@@

    RIMPA0114 & 699908 & Michoacan & 6     & 0.17 & 0.83 \\

@@

    RIMPA0118 & 699912 & Mexico & 6     & 0.17 & 0.83 \\

@@

    RIMPA0142 & 699936 & Colima & 18    & 0.44 & 0.56 \\

@@

    RIMPA0155 & N/A   & Jalisco & 73    & 0.01 & 0.99 \\

@@

    RIMPA0157 & N/A   & Jalisco & 58    & 0.34 & 0.66 \\
    RIMPA0158 & N/A   & Jalisco & 64    & 0.53 & 0.47 \\

@@

% Table S4. PCs for BayEnv
